### 2019-02-18 manuscript/introduction.tex
- new paragraph(s) in introduction, and matching citations - new title ideas or modifications

Polyploidization changes the genomic content of all cells, and consequently has the potential to affect a wide variety, if not all traits. 
Among the many of changes associated with polyploidization, perhaps the most prominent is the association between polyploidy and propensity for self-fertilization \citep{stebbins_1950, grant_1956, barrett_1988}.
Polyploidization is not only suspected of a mere correlated change in breeding systems, but of a causal link.
By disrupting certain genetic self-incompatibility systems, polyploidy is also associated with the ability to self-fertilize in many plant groups (Miller and Venable, 2000; Mable, 2004; Robertson et al., 2011).
% It's not Spencer's best line, but it's not bad for our work: Barrett 2008: Because polyploidy affects the entire genome, it is perhaps not surprising that it influences many aspects of the phenotype, including the mating system. However, although it has long been recognized that the evolutionary transition from diploidy to polyploidy may result in correlated changes in mating patterns, the theoretical and empirical evidence is limited and often contradictory. 
%
% how polyploidy breaks down SI
% how that generates associations (and variable associations of mating system and ploidy! husband2008, others cited by barrett_2013

% Breeding systems also affect diversification rate and so there could be an interaction
% we also have this great data for SI loci and the transition could be even more common, providing power to resolve the great diversification questions
% set up pathways

>>>>

Polyploidization changes the genomic content of all cells, and consequently has the potential to affect a wide variety, if not all, traits. 
Among the many of changes associated with polyploidization, perhaps the most prominent is the association between polyploidy and propensity for self-fertilization \citep{stebbins1950, barrett1988}.
Polyploidy is not only a suspected correlate of breeding systems but a causal link \citep{stout1942, lewis1947}.
Doubled number of alleles in pollen is strongly suspected to effect disruption of the genetic mechanisms in gametophytic self-incompatibility systems \citep{entani1999, tsukamoto2005, kubo2010}. 
Polyploidy is also thought to be associated with changes in the rate of self-fertilization, although the evidence for this correlated shift in mating system appears limited and sometimes contradictory \citep{barringer2007, barrett2008, husband2008}.
% It's not Spencer's best line, but it's not bad for our work: Barrett 2008: "Because polyploidy affects the entire genome, it is perhaps not surprising that it influences many aspects of the phenotype, including the mating system. However, although it has long been recognized that the evolutionary transition from diploidy to polyploidy may result in correlated changes in mating patterns, the theoretical and empirical evidence is limited and often contradictory."
% how that generates associations (and variable associations of mating system and ploidy! husband2008, others cited by barrett2013
Breeding system shifts---changes in the collection of physiological and morphological traits that determine the likelihood that any two gametes unite---are remarkably common and affect the distribution and amount of genetic variation in populations \citep{stebbins1974,barrett2013}.
They are by themselves thought to have a broad effect on other traits. 
The frequent transition from self-incompatibility (SI) to self-compatibility (SC) is strongly associated with net diversification rate changes \citep{goldberg_2010,devos2014}.
Given that  changes in ploidy and breeding systems may be causally related and have profound profound affects on the fate of lineages, it seems particularly profitable to examine whether and how their macroevolutionary effects interact.
%
% we also have this great data for SI loci and the transition could be even more common, providing power to resolve the great diversification questions
%
% set up pathway dependence
